---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---


We are going to make some plotly plots. 

## load packages and data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

Let's get some data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    borough = neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    borough == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

Let's make a scatterplot

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  #This is creating new variable using the str_c(string_conbine) function to combine variables together as a text option. eg. "Price: $165\nRating: 4.5"
  #"\n" will create text in a different lane. 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```
`x = ~lat, y = ~long` tells the variables for the x and y axis. 
`color = ~price` tells to differ the colors of the markers by `price`. 
`text = ~text_label` is showing that newly created text variable when you hovering at the point. 

Let's make a boxplot. 
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  #This is to get rid of the alphabetic order of neighbourhood, but order it according to "price" instead. 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```


Let's make a bar plot. 
```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  #this is to count how many there are for each neighbourhood. 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```


## ggplotly
```{r}
scatter_ggplot = 
  nyc_airbnb %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
```

In this way, you are making a ggplot first, then you are using `ggplotly` tp turn it into an interactive graphic, but this will be so slow. You would still want to use `plot_ly`. 


## Create a Dashboard...

Not in this docuemnt. 